\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
revision of attack related work

\subsection{USB Attack}
\label{subsec:usb_attack}
\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices. In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, accurate attacks couldn't be performed due to lack of user interface (UI). One means of attack is to crash the operating system with the property that the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique. But code injection and data exfiltrating would not work here.

\textbf{Attacks based on code injection and data exfiltrating: } \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain, stuxnet, conficker,flame} also attack with code injection. \cite{webcam, malware, audioextraction, usbee, turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices. Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.

\textbf{Attacks based on protocol masquerading:} Protocol masquerading is widely used to hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}. These works try to hide their own functionality with the re-written firmware when they are connected to the host, software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter. Due to the limitations of USB 2.0, there is no port for video transferring in the devices with USB 2.0, accurate attacks could not be performed without real-time feedback from the host, only environment fitted commands and scripts will work in these scenarios. \cite{JFC} is to automatically record phone-screen and monitor user's input based on the Mobile High-Definition Link(MHL) standard. With this approach, it is able to successfully exfiltrate data without the permission on user's side. Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.

\textbf{Attacks based on physical signal recovering:} Physical radio frequency always contains sensitive data, \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer. In a similar way, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

>>>>

\subsection{USB Attack}
\label{subsec:usb_attack}
\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading. Here we will introduce them following an order of their category.

From the kernel perspective, its USB software stack generally expects devices to follow the USB standard and may not consider corner cases of malformed USB packets. Based on this, Facedancer\cite{facedancer} and Syzkaller\cite{syzkaller} uses fuzzing technique to uncover the bugs lying in the kernel drivers. These bugs can cause kernel crash and lead to a DoS situation. Though this poses a great challenge to the availability of a system, this attack still requires physical access to the host and is unable to cause more damage other than DoS.

In the field of USB security, protocol masquerading is also a widely used attack scheme. Due to the lack of authentication in USB protocol, malicious devices can hide their real functionality with re-written firmware\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}. These works rewrite the firmware of a normal-looking flash drive, which allows it to pretend as other devices. When these modified drives are connected to the host, they will be recognized as keyboard or mouse. Then the attacker can execute malicious payloads as they were using the victim's devices. But due to the limitation of USB 2.0\cite{usb20} protocol, these BadUSB attacks are unable to obtain video feedback from the victim as video were not supported until USB 3.0 \cite{usb30}. Though USB 2.0 does not support video transmission, there exists a protocol called MHL(Mobile High-Definition Link) which extends the USB standard and allow video signal to be transmitted through USB interface. JFC\cite{JFC}, short for juicy filming charging is such a work which abuses this standard and exfiltrate video data from victim without permission. But in JFC, this data exfiltration is not combined with BadUSB attacks and MHL is an outdated standard, which limits its capability.

Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means. Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device and uses a zero-day exploit\cite{zero-day} to execute the malware automatically. There are also works like \cite{brain, stuxnet, conficker,flame} following the same paradigm and performing code-injection attacks. These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.

As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information. Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data. In a similar fashion, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
